Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-11 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updates supp.tex

%----------------------------------------
\documentclass[aps, prl]{revtex4-2}  % for review and submission
%\usepackage{graphicx}  % needed for figures
%\usepackage{dcolumn}   % needed for some tables
%\usepackage{bm}        % for math
%\usepackage{amssymb}   % for math
%\usepackage[hidelinks]{hyperref}
%\usepackage{fancyhdr}
%\usepackage{xcolor}
%\usepackage{grffile}
%\usepackage[top=1in,left=0.8in, right=0.8in, bottom=0.8in]{geometry}
%\usepackage{float}
%\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{2ex}{2ex}

\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage{amsmath}   % for math
\usepackage[top=0.85in,left=0.9in, right=0.9in, bottom=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\usepackage[compact]{titlesec}

@@

\begin{document}
\title{Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta}
\maketitle
\section{\large Spectrometer Acceptance}
\noindent The $^{1}$H$(e,e'p)$ coincidence elastic reaction was used (at kinematics very similar to the deuteron 80 MeV/c setting) to check of the spectrometers'
acceptance model\cite{COSY} using the simulation program, SIMC. The proton form factor parametrization of Ref.\cite{PhysRevC.69.022201} was used. \\
\indent Figures \ref{fig:fig1} and \ref{fig:fig2} show the spectrometers' reconstructed quantities ($\delta$,  $Y_{\mathrm{tar}}$, $Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$)
where $\delta$ is the momentum fraction defined as $\delta = \frac{P-P_{0}}{P_{p}}$, where $P$ is the particle momentum and $P_{0}$ is the spectrometer central momentum.
The $Y_{\mathrm{tar}}$ is the reconstructed trajectory along the spectrometer $y-$coordinate, and ($Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$) are the reconstructed trajectories
tangent to the spectrometer central optics axis ($+z$) and are defined as $Y'_{\mathrm{tar}} = \frac{dY_{\mathrm{tar}}}{dz}$ and $X'_{\mathrm{tar}} = \frac{dX_{\mathrm{tar}}}{dz}$.
See Section 4.4 of Ref.\cite{cyero_phdthesis} for a more detailed description of these quantities.\\
\begin{figure}[h]
\includegraphics[scale=0.36]{plots/hms_acc_3288.png}
\caption{HMS reconstructed quantities ($\delta$,  $Y_{\mathrm{tar}}$, $Y'_{\mathrm{tar}}$, $X'_{\mathrm{tar}}$) at the target reaction vertex using $^{1}$H$(e,e'p)$.
  For each reconstructed quantity, the top panel shows a comparison between data (blue) and SIMC (red) with their respective integrated charge-normalized yields
  and the data-to-SIMC ratio numerical values (top-left corner). The bottom panel shows the data to SIMC yield ratio (Y$_{\mathrm{data}}$/Y$_{\mathrm{SIMC}}$) on a
  bin-by-bin basis, where the inner (black) and outer (blue) dashed lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}
\label{fig:fig1}
\includegraphics[scale=0.36]{plots/shms_acc_3288.png}
\caption{Same as Fig. \ref{fig:fig1}, but for SHMS. }
\label{fig:fig2}
\section{\large Event Selection Cuts}
\noindent Figures \ref{fig:fig3}-\ref{fig:fig7} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
The black dashed or red solid lines (for collimators) represent the cuts or geometrical (collimators) boundaries used to select true $^{2}$H$(e,e'p)n$ coincidence events.
The exact same cuts were also applied to the 580 and 750 MeV/c settings. The data yield has been normalized by the total charge and corrected for the inefficiencies described in the Letter.
The FSI model from J.M. Laget was used in the simulation for the plots shown below.
\includegraphics[scale=0.30]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
\caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
\label{fig:fig3}

@@

\includegraphics[scale=0.33]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
\caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
  Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$}
\label{fig:fig4}
\includegraphics[scale=0.30]{plots/coin_and_eCal_CUT_80MeV_35deg.png}

@@

\label{fig:fig5}
\includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_data.png}

@@

\label{fig:fig6}
\includegraphics[scale=0.30]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
\caption{Same as Fig. \ref{fig:fig6}, but for simulation.}
\label{fig:fig7}

@@

\noindent Figures \ref{fig:fig8} and \ref{fig:fig9} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.

@@

\includegraphics[scale=0.4]{plots/d2_kin_thnq35.png}

@@

\label{fig:fig8}
\includegraphics[scale=0.35]{plots/d2_kin_thnq45.png}
\caption{Same as Fig. \ref{fig:fig8}, but for $\theta_{nq}=45^{\circ}$}
\label{fig:fig9}

@@

\indent Figure \ref{fig:fig10} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified

@@

\includegraphics[scale=0.35]{plots/tgt_bkg_d2_pm580_allthnq.png}

@@

\label{fig:fig10}

@@

kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:fig11}. The calculation was done using the

@@

\includegraphics[scale=0.40]{plots/RC_factor.png}

@@

\label{fig:fig11}

@@

Fig. \ref{fig:fig12}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.

@@

\includegraphics[scale=0.40]{plots/BC_factor.png}

@@

\label{fig:fig12}

@@

    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{bc,1}} - \sigma^{\mathrm{exp}}_{\mathrm{bc,2}}, \\
    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{bc,2}})^{2},

@@

\indent Figure \ref{fig:fig13} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
In Fig. \ref{fig:fig13}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,

@@

\includegraphics[scale=0.4]{plots/Em_syst.png}

@@

\label{fig:fig13}

@@

\includegraphics[scale=0.33]{plots/rad_sys.png}

@@

\label{fig:fig14}
\includegraphics[scale=0.33]{plots/bc_sys.png}
\caption{Same as Fig. \ref{fig:fig14} but for bin-centering corrections.}
\label{fig:fig15}

@@

Figures \ref{fig:fig14} and \ref{fig:fig15} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that

@@

kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:fig16} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in

@@

\includegraphics[scale=0.38]{plots/Pr_and_Ps.png}

@@

\label{fig:fig16}

@@

%\clearpage
\bibliography{supp}

>>>>

%----------------------------------------
\documentclass[aps, prl]{revtex4-2}  % for review and submission
%\usepackage{graphicx}  % needed for figures
%\usepackage{dcolumn}   % needed for some tables
%\usepackage{bm}        % for math
%\usepackage{amssymb}   % for math
%\usepackage[hidelinks]{hyperref}
%\usepackage{fancyhdr}
%\usepackage{xcolor}
%\usepackage{grffile}
%\usepackage[top=1in,left=0.8in, right=0.8in, bottom=0.8in]{geometry}
%\usepackage{float}
%\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{2ex}{2ex}
\usepackage{comment}
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage{amsmath}   % for math
\usepackage[top=0.85in,left=0.9in, right=0.9in, bottom=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\usepackage[compact]{titlesec}

@@

\begin{document}
\title{Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta}
\maketitle
\section{\large Event Selection Cuts}
\noindent Figures \ref{fig:Em_Q2_cuts}-\ref{fig:simc_coll_cuts} show the event selection cuts for data (blue hatched) and SIMC (red data points) for the deuteron 80 MeV/c kinematic setting at $\theta_{nq}=35\pm5^{\circ}$.
The black dashed or red solid lines (for collimators) represent the cuts or geometrical (collimators) boundaries used to select true $^{2}$H$(e,e'p)n$ coincidence events.
The exact same cuts were also applied to the 580 and 750 MeV/c settings. Each histogram has all the other event selection cuts described except a self cut.
The integrated counts (within the cut boundary) for data and simulation as well as the data-to-simulation yield ratio is shown (top left) for each selection cut.
The data yield has been normalized by the total charge and corrected for the inefficiencies described in the Letter. The FSI model from J.M. Laget was used in the simulation for the plots shown below.
\begin{figure}[!h]
\includegraphics[scale=0.25]{plots/Em_and_Q2_CUT_80MeV_35deg.png}
\caption{Event selection cuts on missing energy (left) and 4-momentum transfer (right).}
\label{fig:Em_Q2_cuts}
\includegraphics[scale=0.25]{plots/deltaAcc_and_ZtarCUT_80MeV_35deg.png}
\caption{Acceptance cut on HMS momentum fraction (left) and event selection cut on the difference between the $z$-reaction vertex on both spectrometers (right).
  Inset (left): The SHMS momentum acceptance range.}
\label{fig:delta_Ztar_cuts}
\end{figure}\\
\indent Figure \ref{fig:Em_Q2_cuts} (left) shows the primary cut used to select true $^{2}\mathrm{H}(e,e'p)n$ coincidence events by requiring a missing
energy cut around the deuteron binding energy ($\sim$2.2 MeV) using the missing energy formula described in the Letter, where the
recoiling system is assumed to be a neutron. The peak is not exactly at the deuteron binding energy because energy loss corrections have not
been applied to the data nor SIMC. Figure \ref{fig:Em_Q2_cuts} (right) shows a kinematical cut made on the 4-momentum transfer at $Q^{2} = 4.5\pm0.5$ (GeV/c)$^{2}$
to select events only at the highest possible momentum transfers to further suppress MEC and IC. \\
\indent Figure \ref{fig:delta_Ztar_cuts} (left) shows a momentum acceptance ($\delta$) cut made on the HMS in the range $8\%\leq\delta\leq8\%$, where the optics reconstruction
is reliable and well understood from previous experiments in the 6 GeV era. The inset shows the SHMS momentum acceptance which was constrained by that of the HMS to be
$|\delta|\lesssim$3$\%$ which is well within the reliable SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$. Figure \ref{fig:delta_Ztar_cuts} (right) shows reaction vertex cut
on the difference between the HMS and SHMS reconstructed reaction vertices along the $z$-coordinate (target length). The cut is made at $\pm2$ cm relative to the histogram peak.
If the events originated from the same reaction vertex (i.e., true coincidences), the difference should peak at zero with a finite resolution width. If the events are uncorrelated
(i.e., accidental coincidences), however, the reconstruction along the $z_{\mathrm{v}}$-vertex can vary significantly between the two spectrometers, which contribute to the tails of the
distribution.

@@

\includegraphics[scale=0.25]{plots/coin_and_eCal_CUT_80MeV_35deg.png}

@@

\label{fig:coin_ecal_cuts}
\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_data.png}

@@

\label{fig:data_coll_cuts}
\includegraphics[scale=0.25]{plots/collimator_CUT_80MeV_35deg_SIMC.png}
\caption{Same as Fig. \ref{fig:data_coll_cuts}, but for simulation.}
\label{fig:simc_coll_cuts}

@@

\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.

@@

\includegraphics[scale=0.3]{plots/d2_kin_thnq35.png}

@@

\label{fig:d2_kin_35deg}
\includegraphics[scale=0.3]{plots/d2_kin_thnq45.png}
\caption{Same as Fig. \ref{fig:d2_kin_35deg}, but for $\theta_{nq}=45^{\circ}$}
\label{fig:d2_kin_45deg}

@@

\indent Figure \ref{fig:tgt_wall} shows the missing energy spectrum for the 580 MeV/c setting (left) and the corresponding reconstructed SHMS $z$-vertex (right) for the specified

@@

\includegraphics[scale=0.3]{plots/tgt_bkg_d2_pm580_allthnq.png}

@@

\label{fig:tgt_wall}

@@

kinematic bin as described in the Letter. The radiative correction factors for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ are shown in Fig. \ref{fig:RC_factor}. The calculation was done using the

@@

\includegraphics[scale=0.30]{plots/RC_factor.png}

@@

\label{fig:RC_factor}

@@

Fig. \ref{fig:BC_factor}. The calculation was done using the Laget PWIA and FSI models for systematic effect studies, but the FSI model was ultimately used to correct the data cross section.

@@

\includegraphics[scale=0.30]{plots/BC_factor.png}

@@

\label{fig:BC_factor}

@@

    &\Delta \equiv \sigma^{\mathrm{exp}}_{\mathrm{1}} - \sigma^{\mathrm{exp}}_{\mathrm{2}}, \\
    &\sigma^{2}_{\Delta} \equiv (\delta\sigma^{\mathrm{exp}}_{\mathrm{1}})^{2} - (\delta\sigma^{\mathrm{exp}}_{\mathrm{2}})^{2},

@@

\indent Figure \ref{fig:Em_sys} below shows an example of the systematic effects on the missing energy cut for $\theta_{nq}=35^{\circ}$ and $45^{\circ}$ over the full $p_{\mathrm{r}}$ range.
In Fig. \ref{fig:Em_sys}, the different color groups represent the Barlow ratio evaluated at difference between the subset and full missing energy cut range. For mostly the entire momentum range,

@@

\includegraphics[scale=0.3]{plots/Em_syst.png}

@@

\label{fig:Em_sys}

@@

\includegraphics[scale=0.3]{plots/rad_sys.png}

@@

\label{fig:rad_sys}
\includegraphics[scale=0.3]{plots/bc_sys.png}
\caption{Same as Fig. \ref{fig:rad_sys} but for bin-centering corrections.}
\label{fig:bc_sys}

@@

Figures \ref{fig:rad_sys} and \ref{fig:bc_sys} show the Barlow ratio for radiative and bin-centering systematics is mostly within 2 standard deviations which show that

@@

kinematic bin in ($\theta_{nq}$, $p_{\mathrm{r}}$). For illustration purposes, Fig. \ref{fig:Pm_Ps} shows the experimental data yield (left) and the spectrometers' phase space volume (right) binned in

@@

\includegraphics[scale=0.3]{plots/Pr_and_Ps.png}

@@

\label{fig:Pm_Ps}

@@

%\clearpage
\bibliography{supp}
